### 2019-07-15 draft_charts.Rmd
Change legend in chart 2 and title in chart 7

#' rename_cohort
#'
#' @param x a vector with cohorts
#'
#' @return a vector of renamed cohorts
rename_cohort <- function(x, two_lines = TRUE) {
  if (two_lines == TRUE) {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers\n(1936—1945)", 
      `1946-1955` = "Early boomers\n(1946—1955)", 
      `1956-1965` = "Late boomers\n(1956—1965)", 
      `1966-1975` = "Gen Xers\n(1966—1975)", 
      `1976-1985` = "Xennials\n(1976—1985)")

    factor(cohort, levels = c("Pre-boomers\n(1936—1945)", 
                              "Early boomers\n(1946—1955)", 
                              "Late boomers\n(1956—1965)", 
                              "Gen Xers\n(1966—1975)", 
                              "Xennials\n(1976—1985)"))
  } else {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers (1936—1945)", 
      `1946-1955` = "Early boomers (1946—1955)", 
      `1956-1965` = "Late boomers (1956—1965)", 
      `1966-1975` = "Gen Xers (1966—1975)", 
      `1976-1985` = "Xennials (1976—1985)")

    factor(cohort, levels = c("Pre-boomers (1936—1945)", 
                              "Early boomers (1946—1955)", 
                              "Late boomers (1956—1965)", 
                              "Gen Xers (1966—1975)", 
                              "Xennials (1976—1985)"))
  }
}

@@

```{r theme2}
chart4 <- read_csv("data/figure4.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(lifetime_earn_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 1), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

@@

# create the output plot
plotr(titler("Retirement incomes may fall short for about 4 in 10 Xennials if policymakers ignore Social Security’s financing gap"),
      subtitler("Share of adults unable to replace 75 percent of their preretirement earnings at age 70 "),
      chart9,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("The analysis compares per capita family income at age 70 to average annual earnings received from ages 50 to 59, both measured in constant 2018 dollars as adjusted by the change in the consumer price index. The income measure at age 70 includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, and the annual income from an annuity valued at 80 percent of financial assets (including retirement accounts). The analysis computes a per capita measure by dividing total family income by two for married people.", width = 131),
      heights = c(6.5, 1.5, 30, 1, 1, 5))
```

@@

# create the output plot
plotr(titler("A 25 percent Social Security benefit cut could leave about 1 in 12 Gen X and Xennial retirees in poverty"),
      subtitler("Percentage of adults with incomes below the federal poverty level at age 70 "),
      chart12,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("The analysis compares family income from Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, rent, retirement account withdrawals, and income from coresident family members to the federal poverty level. "),
      heights = c(4, 1.5, 30, 1, 1, 3))
```

@@

# create the output plot
plotr(titler("Although retirement incomes are projected to rise for people of color, they will continue to lag far behind incomes for non-Hispanic white people"),
      subtitler("Median annual per capita after-tax family income at age 70 (constant 2018 dollars)"),
      chart6,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("This income measure includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, capital gains, and retirement account withdrawals, minus payroll taxes, federal and state income taxes, and Medicare surtaxes. The analysis computes a per capita measure by dividing total family income by two for married people. The analysis assumes that scheduled Social Security benefits are paid. The chart excludes other racial groups because of small sample sizes."),
      heights = c(6.5, 1.2, 28, 1, 1, 4.5))
```

@@

```{r, theme8}
chart3b <- read_csv("data/figure3b.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%  
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(Ownssb_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

>>>>

#' rename_cohort
#'
#' @param x a vector with cohorts
#'
#' @return a vector of renamed cohorts
rename_cohort <- function(x, two_lines = TRUE) {
  if (two_lines == TRUE) {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers\n(1936–1945)", 
      `1946-1955` = "Early boomers\n(1946–1955)", 
      `1956-1965` = "Late boomers\n(1956–1965)", 
      `1966-1975` = "Gen Xers\n(1966–1975)", 
      `1976-1985` = "Xennials\n(1976–1985)")

    factor(cohort, levels = c("Pre-boomers\n(1936–1945)", 
                              "Early boomers\n(1946–1955)", 
                              "Late boomers\n(1956–1965)", 
                              "Gen Xers\n(1966–1975)", 
                              "Xennials\n(1976–1985)"))
  } else {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers (1936–1945)", 
      `1946-1955` = "Early boomers (1946–1955)", 
      `1956-1965` = "Late boomers (1956–1965)", 
      `1966-1975` = "Gen Xers (1966–1975)", 
      `1976-1985` = "Xennials (1976–1985)")

    factor(cohort, levels = c("Pre-boomers (1936–1945)", 
                              "Early boomers (1946–1955)", 
                              "Late boomers (1956–1965)", 
                              "Gen Xers (1966–1975)", 
                              "Xennials (1976–1985)"))
  }
}

@@

```{r theme2}
chart4 <- read_csv("data/figure4.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Men",
                       `2.Female` = "Women")) %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(lifetime_earn_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 1), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

@@

# create the output plot
plotr(titler("Retirement incomes may fall short for about 4 in 10 Xennials if policymakers ignore Social Security’s financing gap"),
      subtitler("Share of adults unable to replace 75 percent of their preretirement earnings at age 70"),
      chart9,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("The analysis compares per capita family income at age 70 to average annual earnings received from ages 50 to 59, both measured in constant 2018 dollars as adjusted by the change in the consumer price index. The income measure at age 70 includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, and the annual income from an annuity valued at 80 percent of financial assets (including retirement accounts). The analysis computes a per capita measure by dividing total family income by two for married people.", width = 131),
      heights = c(6.5, 1.5, 30, 1, 1, 5))
```

@@

# create the output plot
plotr(titler("A 25 percent Social Security benefit cut could leave about 1 in 12 Gen X and Xennial retirees in poverty"),
      subtitler("Share of adults with incomes below the federal poverty level at age 70 "),
      chart12,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("The analysis compares family income from Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, rent, retirement account withdrawals, and income from coresident family members to the federal poverty level. "),
      heights = c(4, 1.5, 30, 1, 1, 3))
```

@@

# create the output plot
plotr(titler("Although retirement incomes are projected to rise for people of color, they will continue to lag far behind incomes for white people"),
      subtitler("Median annual per capita after-tax family income at age 70 (constant 2018 dollars)"),
      chart6,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("This income measure includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, capital gains, and retirement account withdrawals, minus payroll taxes, federal and state income taxes, and Medicare surtaxes. The analysis computes a per capita measure by dividing total family income by two for married people. The analysis assumes that scheduled Social Security benefits are paid. The chart excludes other racial groups because of small sample sizes."),
      heights = c(6.5, 1.2, 28, 1, 1, 4.5))
```

@@

```{r, theme8}
chart3b <- read_csv("data/figure3b.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Men",
                       `2.Female` = "Women")) %>%  
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(Ownssb_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()
